Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2019-04-27 paper/paper.tex
added Alistair edits

The 150 cells for which we called the full viral genotypes are shown in \FIG{genotypes}.
Visual inspection of this figure reveals a wealth of information.
For instance, the cell with the highest viral burden (\textit{cell 1} in \FIG{genotypes}, which has 65\% of its mRNA from virus) was infected by a virion that expressed unmutated copies all eight genes and did not induce detectable IFN.
But 12 of the other 13 cells with at least 50\% of their mRNA from virus were infected by virions that had a mutation or failed to express a gene, and five of these cells produced IFN.
As expected, all cells infected by virions that failed to express a component of the viral polymerase complex (PB2, PB1, PA, or NP) expressed low amounts of viral mRNA since they are limited to primary transcription off the incoming proteins (e.g., \textit{cell 132} and \textit{cell 143}).
The two cells that expressed the most IFN (\textit{cell 13} and \textit{cell 123}) lacked the viral NS gene that encodes the virus's primary IFN antagonist~\cite{garcia1998influenza, hale2008multifunctional}.
Many other IFN+ cells had different defects such as large internal deletions (e.g., \textit{cell 5} and \textit{cell 89}) or amino-acid mutations (e.g., \textit{cell 9}, \textit{cell 28}, and many others).

>>>>

The 150 cells for which we called the full viral genotypes are shown in \FIG{genotypes}.
Visual inspection of this figure reveals a wealth of information.
For instance, the cell with the highest viral burden (\textit{cell 1} in \FIG{genotypes}, which has 65\% of its mRNA from virus) was infected by a virion that expressed unmutated copies all eight genes and did not induce detectable IFN.
But 12 of the other 13 cells with at least 50\% of their mRNA from virus were infected by virions that had a mutation or failed to express a gene, and five of these cells produced IFN.
As expected, all cells infected by virions that failed to express a component of the viral polymerase complex (PB2, PB1, PA, or NP) expressed low amounts of viral mRNA since they are limited to primary transcription using incoming proteins (e.g., \textit{cell 132} and \textit{cell 143}).
The two cells that expressed the most IFN (\textit{cell 13} and \textit{cell 123}) lacked the viral NS gene that encodes the virus's primary IFN antagonist~\cite{garcia1998influenza, hale2008multifunctional}.
Many other IFN+ cells had different defects such as large internal deletions (e.g., \textit{cell 5} and \textit{cell 89}) or amino-acid mutations (e.g., \textit{cell 9}, \textit{cell 28}, and many others).
